INTELLIGENT SYSTEMS

### 2021-04-11 slides/slides_paper6.tex
start foreground

\begin{frame}{THE PROPOSED APPROACH - \emph{Coarse Mask Generation}}
    \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{0.45\linewidth}
            A CNN network\footnotemark is used to be able 
            to extract a first coarse mask. 
            Unfortunately, as can be seen in 
            the image, the generated masks 
            appear to be inaccurate and do 
            not comply with the position of 
            the underlying object.
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[h!]
                \centering
                \includegraphics[width = 1 \linewidth]{images/paper6/coarse mask.png}
                \centering
            \end{figure}
        \end{minipage}
    \end{minipage}
    \footnotetext{I. Croitoru, S.-V. Bogolin, and M. Leordeanu, “Unsupervised learning from video to detect foreground objects in single images,” in Proc. IEEE Int. Conf. Comput. Vis. (ICCV), Oct. 2017, pp. 4335–4343.}
\end{frame}

>>>>

\begin{frame}{THE PROPOSED APPROACH - \emph{Coarse Mask Generation}}
    \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{0.45\linewidth}
            A CNN network\footnotemark ~is used to be able 
            to extract a first coarse mask. 
            Unfortunately, as can be seen in 
            the image, the generated masks 
            appear to be inaccurate and do 
            not comply with the position of 
            the underlying object.
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[h!]
                \centering
                \includegraphics[width = 1 \linewidth]{images/paper6/coarse mask.png}
                \centering
            \end{figure}
        \end{minipage}
    \end{minipage}
    \footnotetext{I. Croitoru, S.-V. Bogolin, and M. Leordeanu, “Unsupervised learning from video to detect foreground objects in single images,” in Proc. IEEE Int. Conf. Comput. Vis. (ICCV), Oct. 2017, pp. 4335–4343.}
\end{frame}

\begin{frame}{THE PROPOSED APPROACH - \emph{Coarse Mask Enhancement}}
    To carry out the enhanced coarse mask, the unsupervised GrubCut 
    model\footnotemark ~is used. To achieve mask optimization, the 
    method performs the following two steps:
    \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{0.45\linewidth}
            \begin{enumerate}
                \item search for the smallest bounding box inside the mask.
                \item enhance the mask based on the previously created bounding box and on the RGB image.
            \end{enumerate}
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[h!]
                \centering
                \includegraphics[width = 1.2 \linewidth]{images/paper6/enhancement.png}
                \centering
            \end{figure}
        \end{minipage}
    \end{minipage}
    \footnotetext{C. Rother, V. Kolmogorov, and A. Blake, “GrabCut: Interactive foreground extraction using iterated graph cuts,” ACM Trans. Graph., vol. 23, no. 3, pp. 309–314, 2004.}
\end{frame}

\begin{frame}{THE PROPOSED APPROACH - \emph{Recursive Mask Refinement}}
    A network called DeepLab \footfullcite{0876055502} is used for semantic segmentation. This 
    network uses the mask generated by the GrubCut method and, through a 
    comparison on the original image, produces a new better mask that will 
    be used as a new training set. The best mask will be obtained after a 
    maximum of 5 training rounds.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 1 \linewidth]{images/paper6/DeepLab.png}
        \centering
    \end{figure}
\end{frame}
